An open reproducible framework for the study of the iterated prisoner's dilemma

### 2015-11-03 tex/paper.tex
Some material for the introduction, corrected citation.

@@

\begin{itemize}
    \item To enable the reproduction of previous Iterated Prisoner's Dilemma
    research as easily as possible.
    \item To produce the de-facto tool for any future Iterated Prisoner's
    Dilemma research.
    \item To provide as simple a means as possible for anyone to define and
    contribute new and original Iterated Prisoner's Dilemma strategies.
\end{itemize}

@@

\begin{itemize}
    \item Open: all code is released under an MIT license;
    \item Reproducible: at the time of writing there is an excellent level of
        integrated tests with 99.59\% coverage;
    \item Documented: all features of the library are documented for ease of
        use.
    \item Extensive: over 100 strategies are included.
\end{itemize}

>>>>

Several iterated prisoner's dilemma tournaments have generated much interest,
including Axelrod's original tournaments, two 2004 anniversary tournaments, and
the S&P 2012 tournament following the discovery of zero-determinant strategies.
Subsequent research has spawned an enormous number of papers, but rarely are the
results reproducible. Among well-known tournaments, in only one case is the full
original source code available (Axelrod's second tournament, in FORTRAN); in no
cases is the available code well-documented, easily modifiable, or released
with significant test suites.

To make matters more complicated, often a newly-created strategy is studied in
isolation by opponents chosen by the strategy's creators, and often such
strategies are not sufficiently described to enable realiable recreation
(in the absense of source code), with \cite{slany2007some} being a notable
counter-example. In some cases strategies are revised without updates to their
names or published implementations \cite{li2007design} \cite{li2011engineering}.
As a result, some of the results related to these strategies and tournaments
have not been reliably replicated, and have not met the basic scientific
criterion of falsifiability.

@@

\begin{itemize}
    \item To enable the reproduction of Iterated Prisoner's Dilemma
    research as easily as possible
    \item To produce the de-facto tool for any future Iterated Prisoner's
    Dilemma research
    \item To provide as simple a means as possible for anyone to define and
    contribute new and original Iterated Prisoner's Dilemma strategies
\end{itemize}

@@

\begin{itemize}
    \item Open: all code is released under an MIT license;
    \item Reproducible and well-tested: at the time of writing there is an excellent level of
        integrated tests with 99.59\% coverage
    \item Well-documented: all features of the library are documented for ease of
        use and modification
    \item Extensive: over 100 strategies are included, with infinitely-many
    strategies available in the case of parameterized strategies
    \item Extensible: easy to modify to include new strategies and to run new tournaments
\end{itemize}
